Quality Metrics for SKOS Vocabularies

### 2012-03-13 background.tex
structured section 2

% About Controlled Vocabulary Quality

@@

%SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.

>>>>

% About Quality in SKOS vocabularies

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.

The quality of a given SKOS vocabulary can have a direct impact on the following application areas of controlled vocabularies: \todo{CM}{write a paragraph}

SKOS consistency and integrity means that
-

@@

### 2012-03-13 introduction.tex
structured section 2

The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies. We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and \textbf{formalized} them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.

>>>>

The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies. They can be used by domain experts and vocabulary designers for judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified existing \textbf{quality criteria} for controlled vocabularies by examining existing guidelines and formalized them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.
